---
title: "HSCT Participant Numbers"
author: "Matt Kmiecik"
date: "Last update: `r format(Sys.Date(), format = '%d %B %Y')`"
output: 
  html_document:
    theme: journal
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

This document specifies how the participant numbers for the Hayling Sentence Completion Test (HSCT) control study were determined/created.

Here are the packages needed:

```{r}
library(tidyverse)
```

A random 4 digit sequence was generated for each participant and in the following order. Each ID number is unique to each participant. Running the code below will always generate the same id numbers in the same order. 1000 numbers will be generate, just in case:

```{r}
set.seed(18) # Sets the seed for reproducible results
ssid <- sample(1000:9999, 1000, replace = F) # Runs the numbers
ssidData <- tibble(ssid = ssid) # Creates a data frame
write_csv(ssidData, 'hsct-participant-numbers.csv') # Writes out into a *.csv
```

